SSwAB-IT Phase 1 Analysis

### 2025-02-13 Jordana Hoppe/SSwAB-IT/phase_1_analysis.qmd
Update phase_1_analysis.qmd

```{r setup}
#| include: false
library(redcapAPI)
library(tidyverse)
library(gt)
library(gtsummary)
library(caret)
library(eulerr)
```

@@

>>>>

```{r setup}
#| include: false
library(redcapAPI)
library(tidyverse)
library(gt)
library(gtsummary)
library(caret)
library(eulerr)
library(ggpubr)
```

@@

# Manuscript Figures

```{r}
# All pathogens
d <- df[, c("overall_cos", "overall_sos")]
colnames(d) <- c("COS", "SOS")
d <- d[complete.cases(d), ]
a1 <- plot(euler(d == "Positive"),
  quantities = list(cex = 3),
  fills = list(fill = c("#FFC107", "#1E88E5", "#004D40"))
)
a2 <- ggplot(as.data.frame(table(d$COS, d$SOS)), aes(Var1, Var2)) +
  geom_tile(color = "white", fill = "#1E88E5") +
  geom_text(aes(label = paste0(Freq, "\n(", round(Freq / sum(Freq), 3) * 100, "%)")),
    color = "white"
  ) +
  xlab("COS") +
  ylab("SOS") +
  theme_bw() +
  theme(text = element_text(size = 15))
# MRSA
d <- df[, c("staphylococcus_aureus_cos", "staphylococcus_aureus_sos")]
colnames(d) <- c("COS", "SOS")
d <- d[complete.cases(d), ]
b1 <- plot(euler(d == "Positive"),
  quantities = list(cex = 3),
  fills = list(fill = c("#FFC107", "#1E88E5", "#004D40"))
)
b2 <- ggplot(as.data.frame(table(d$COS, d$SOS)), aes(Var1, Var2)) +
  geom_tile(color = "white", fill = "#1E88E5") +
  geom_text(aes(label = paste0(Freq, "\n(", round(Freq / sum(Freq), 3) * 100, "%)")),
    color = "white"
  ) +
  xlab("COS") +
  ylab("SOS") +
  theme_bw() +
  theme(text = element_text(size = 15))
p <- ggarrange(a1, a2, b1, b2, nrow = 2, ncol = 2) +
  bgcolor("White")
ggsave("/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Jordana Hoppe/SSwAB-IT/Dissemination/Figures/fig.png",
  plot = p, width =9, height = 6, units = "in"
)
```
